### 2015-07-09 narrative/data-description.tex
more changes for readability.

\begin{wrapfigure}{r}{0.6\textwidth}
        \vspace{-6ex}
        \begin{centering} 
	\includegraphics[scale=0.8]{graphics/SSIO-bucket.pdf}
        %\vspace{1ex}
        \caption{The system manages the data across the various stages of the data lifecycle}
        \label{fig:ssio-bucket}
        \end{centering}
      % \vspace{-1ex}
\end{wrapfigure}

The assumptions which we will make in choosing a utility function is that:
1) There will only be a small number of priority levels that users will use
to re-prioritize their data; 2) The number of tiers in the storage system will
be small (e.g. NVRAM, PFS, Campaign Storage, HPSS), 3) The default
lifetime of objects in each tier will be specified by the resource by
a tuple (size, lifetime).  The user can then utilize this information to
place information to the system such as: store the highest priority data
as high up on the hierarchy for 6 months, and then migrate this data to tape.
The user can also define the utility for CR files as that they have high
priority but their lifetime is for a short period of time; i.e. when the
next CR file appears on the system or the next two CR files. Research in
describing this utility function will be in conjunction with users
and we will evaluate how policies can be placed in the system and how well
this utility function can be observed by the user.

>>>>

\begin{wrapfigure}{r}{0.6\textwidth}
        \begin{centering} 
	\includegraphics[scale=0.8]{graphics/SSIO-bucket.pdf}
        %\vspace{1ex}
        \caption{The system manages the data across the various stages of the data lifecycle}
        \label{fig:ssio-bucket}
        \end{centering}
      % \vspace{-1ex}
\end{wrapfigure}

%The assumptions which we will make in choosing a utility function is that:
%1) There will only be a small number of priority levels that users will use
%to re-prioritize their data; 2) The number of tiers in the storage system will
%be small (e.g. NVRAM, PFS, Campaign Storage, HPSS), 3) The default
%lifetime of objects in each tier will be specified by the resource by
%a tuple (size, lifetime).  The user can then utilize this information to
%place information to the system such as: store the highest priority data
%as high up on the hierarchy for 6 months, and then migrate this data to tape.
%The user can also define the utility for CR files as that they have high
%priority but their lifetime is for a short period of time; i.e. when the
%next CR file appears on the system or the next two CR files. Research in
%describing this utility function will be in conjunction with users
%and we will evaluate how policies can be placed in the system and how well
%this utility function can be observed by the user.

 We will formulate the concept of utility (from an
application perspective) that is assigned data objects to quantify the
benefits of placement and/or movement actions to application. These
utilities may be based on the importance of the data objects, the frequency
with which they are accessed, etc., and can be used during runtime data
management to evaluate and compare different placement/movement options. 
For example, data objects with higher utility value may be
placed closer (e.g., in faster memory) to the accessing application.
Similarly, when it is time to evict data objects from a higher level storage
layer, the decision about which object to evict may take the utility into
account. Our initial work in defining such a utility is presented in~\cite{tongipdps15}.
 We will also explore autonomic approaches for balancing of the placement and 
 movement of data across the memory hierarchy autonomically, which will be driven 
 by the data utility and will leverage both user hints and information gathered at runtime (e.g., runtime data access
history, network topology, etc.).
Finally, we will explore a complementary notion of utility from a system-wide perspective 
that will capture and quantify, for example, the impact of placement decisions on 
the overall utilization of storage across multiple applications, and will enable system level runtime optimization.

### 2015-07-09 narrative/intro.tex

\begin{table}[htbp]
\small
\vspace{2ex}
\begin{center}
\caption {Relevance to SSIO}
\label{tab:call}
\begin{tabular}{ | p {0.2cm} | p{5cm} | p{7.5cm} | p{2.2cm} |}\hline
\multicolumn{2}{|c|}{\bf Call area} & \multicolumn{1}{|c|}{\bf Relevant S2E2 work} & \multicolumn{1}{|c|}{\bf Proposed research} \\\hline\hline
1 & Data abstractions & Create new APIs  and annotations for users to guide the system for placement  & \S\ref{sec:data-description} \\\hline
2 & Mapping science data models onto hierarchical storage &  Create the ability to re-organize, reduce and prioritize data chunks from an object& \S\ref{sec:data-refactor}, \S\ref{sec:data-description},  \S\ref{sec:managing-data-life}\\\hline
3 & Mechanisms for data movement across the storage hierarchy & Manage data migration based on policies& \S \ref{sec:managing-data-life},  \S\ref{sec:migration} \\\hline
4 &  Extend the interaction of I/O middleware with the resource management system & We will manage data from the application  to the middleware to the storage system and allow them to have an autonomic interaction & \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:naming-discovery}  \\\hline
5 & Design and implement of I/O middleware architectures  & We will create APIs to guide the placement of chunks of data across the SSIO and autonomically move data when necessary& \S\ref{sec:data-description}, \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:naming-discovery} \\ \hline
6 & Approaches to improve the ability of SSIO software to support checkpoint/restart & We will have utility functions defined for the lifetime of data, and allow CR data to be automatically placed in the fastest storage and then purged when it is no longer needed & \S \ref{fig:ssio-bucket}  \\
\hline
\end{tabular}
\end{center}
\vskip -0.5cm
\end{table}

>>>>

\begin{table}[htbp]
\small
\vspace{2ex}
\begin{center}
\caption {Relevance to SSIO}
\label{tab:call}
\begin{tabular}{ | p {0.2cm} | p{5cm} | p{7.5cm} | p{2.2cm} |}\hline
\multicolumn{2}{|c|}{\bf Call area} & \multicolumn{1}{|c|}{\bf Relevant S2E2 work} & \multicolumn{1}{|c|}{\bf Proposed research} \\\hline\hline
1 & Data abstractions & Create new APIs  and annotations for users to guide the system for placement  & \S\ref{sec:data-description} \\\hline
2 & Mapping science data models onto hierarchical storage &  Create the ability to re-organize, reduce and prioritize data chunks from an object& \S\ref{sec:data-refactor}, \S\ref{sec:data-description},  \S\ref{sec:managing-data-life}\\\hline
3 & Mechanisms for data movement across the storage hierarchy & Manage data migration based on policies& \S \ref{sec:managing-data-life},  \S\ref{sec:migration} \\\hline
4 &  Extend the interaction of middleware with the storage system & Manage data from the application  to middleware to the storage system using an autonomic interaction & \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:naming-discovery}  \\\hline
5 & Design and implement of I/O middleware architectures  & Create APIs to guide the placement of chunks of data across the SSIO and autonomically move data& \S\ref{sec:data-description}, \S\ref{sec:managing-data-life}, \S\ref{sec:qos}, \S\ref{sec:naming-discovery} \\ \hline

6 & Approaches to improve the ability of SSIO software to support checkpoint/restart & We will have utility functions defined for the lifetime of data, and allow CR data to be automatically placed in the fastest storage and then purged when it is no longer needed & \S \ref{fig:ssio-bucket}, \S\ref{sec:qos}, \S\ref{sec:managing-data-life}  \\
\hline
\end{tabular}
\end{center}
\vskip -0.5cm
\end{table}
